\documentclass[letterpaper,12pt]{article}

% Include the color package
\usepackage{xcolor}

% Set the default text color to green
\definecolor{PLgreen}{RGB}{29,97,49} 
\definecolor{PLGreenHex}{HTML}{1D6131}
\color{PLGreenHex}

% Optional: Define page margins
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr} % For custom headers

\pagestyle{plain}
\fancyhf{} % Clear default header/footer
\fancyhead[C]{\MakeUppercase{Solverware Policy Letter of 5 March 2025}} % Centered uppercase header
\renewcommand{\headrulewidth}{1pt} % No line under h

% Custom title command for first page only
\newcommand{\policyletter}[2]{%
	\begin{center}
		\vspace*{0.25\baselineskip} % Two lines of whitespace after header
		{\large #1} \\ % Series and number (e.g., MARKETING SERIES 1)
		\vspace{0.5\baselineskip} % Small space between lines
		{\LARGE \textbf{#2}} % Policy name in larger, bold font
		\vspace{\baselineskip} % Space before content
	\end{center}
}

% Document begins
\begin{document}
	% Apply header only to first page
	\thispagestyle{fancy}
	
	% Custom title for first page
	\policyletter{ENGINEERING SOFTWARE SERIES 1}{PRODUCT SPECIFICATIONS}
	
	% Section (all text will be green)
	Whenever a new product is being developed, it is imperative to do adequate planning in the form of functional and technical specifications. These are two separate documents.
	\section{Purpose}
	The most important function of a spec is to design the program. Even if you are working on code all by yourself, and you write a spec solely for your own benefit, the act of writing the spec — describing how the program works in minute detail — will force you to actually design the program.
	\begin{itemize} 
	\item Reason one - you will design the program!
	
	\item Reason two - saves time communicating. When you write a spec, you only have to communicate how the program is supposed to work once!
	
	\item Reason three giant important reason to have a spec is that without a detailed spec, it’s impossible to make a schedule.
	\end{itemize}
	
	\section{Work Hours}
	Regular work hours are from 9:00 AM to 5:00 PM.
	
	\section{Vacation Policy}
	Employees are entitled to 15 days of paid vacation per year.
	
\end{document}