\documentclass[]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{xcolor}

\lstloadlanguages{C,C++,csh,Java}

\definecolor{red}{rgb}{0.6,0,0} 
\definecolor{blue}{rgb}{0,0,0.6}
\definecolor{green}{rgb}{0,0.8,0}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}

\lstset{
	language=csh,
	basicstyle=\footnotesize\ttfamily,
	numbers=left,
	numberstyle=\tiny,
	numbersep=5pt,
	tabsize=2,
	extendedchars=true,
	breaklines=true,
	frame=b,
	stringstyle=\color{blue}\ttfamily,
	showspaces=false,
	showtabs=false,
	xleftmargin=17pt,
	framexleftmargin=17pt,
	framexrightmargin=5pt,
	framexbottommargin=4pt,
	commentstyle=\color{green},
	morecomment=[l]{//}, %use comment-line-style!
	morecomment=[s]{/*}{*/}, %for multiline comments
	showstringspaces=false,
	morekeywords={ abstract, event, new, struct,
		as, explicit, null, switch,
		base, extern, object, this,
		bool, false, operator, throw,
		break, finally, out, true,
		byte, fixed, override, try,
		case, float, params, typeof,
		catch, for, private, uint,
		char, foreach, protected, ulong,
		checked, goto, public, unchecked,
		class, if, readonly, unsafe,
		const, implicit, ref, ushort,
		continue, in, return, using,
		decimal, int, sbyte, virtual,
		default, interface, sealed, volatile,
		delegate, internal, short, void,
		do, is, sizeof, while,
		double, lock, stackalloc,
		else, long, static,
		enum, namespace, string},
	keywordstyle=\color{cyan},
	identifierstyle=\color{red},
	backgroundcolor=\color{white},
}

% Title Page
\title{Leverage Engine Air System Technology - Primary Surface Heat Exchanger }
\author{Mike Stephenson, Solverware}

\lstdefinestyle{sharpc}{language=[Sharp]C, frame=lr, rulecolor=\color{blue!80!black}}

\begin{document}

% \maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}
	this is a test, this is another test.
\section{Test Rig}
\section{Data Analysis}
\subsection{Creating an MS Excel Analysis Spreadsheet}
Data from tests are provided as text files having the CSV format, meaning values are provided in rows with columns separated by columns. Such files use the extension CSV. While CSV file are easily imported into Excel, they are effectively dumb spreadsheets as there are no formulas or calculations. As such, any work done by the spreadsheet would entail editing each spreadsheet to add such functionality. This is impractical when there is more than one spreadsheet to analyze as was the case here.

The solution was to create an application (named PerfTest) that reads the CSV file and creates an actual Excel spreadsheet having the XLSX file extention. This design provides an entry point to add Excel built-in functions into the spreadsheet to analyze the data as well as custom functions to provide physical properties.

The application does several pieces of work:

\begin{enumerate}
	\item Only migrates data of interest as the CSV file has many fields which have nothing to do with heat exchanger performance
	\item Performs unit conversions where appropriate
	\item Adds columns for statistical analysis, including averages of thermocouple readings and standard deviations
	\item Adds columns for physical properties of the heat transfer fluid using custom Excel add-in functions
	\item Adds a page that shows all temperature readings with a check for outliers
	\item Adds data goodness checks such as energy balance calculations
	
\end{enumerate}

It created an Excel pared-down spreadsheet with only performance data kept-in.
Did unit conversions for certain fields.
Added columns for statistical analysis, including average and standard deviations of temperature readings.



\begin{lstlisting}
	using System;
	
	class Program
	{
		static void Main(string[] args)
		{
			Console.WriteLine("Hello, World!");
		}
	}
\end{lstlisting}


\section{Methodology}
\subsection{Statistical Measures}
\subsection{Outlier Detection}
An outlier is defined as a data point that significantly deviates from the rest of the observations in a dataset, often identified as being unusually distant from the mean or median, or not fitting the expected pattern or distribution of the data. Statistically, it can be defined as a value that lies beyond a specified threshold, such as more than 1.5 times the interquartile range (IQR) \footnote{Tukey, J.W., "Exploratory Data Analysis", Addison-Wesley (1977)} from the first or third quartile, or more than two standard deviations from the mean in a normal distribution.


\subsection{Energy Balance Calculations}
In an ideal heat exchanger (no losses), the heat lost by the hot fluid equals the heat gained by the cold fluid: $Q_h=Q_c$. 

%Technically, the most accurate approach is to use the enthalpy difference:
\begin{equation}
	Q_c=m_c(h_{c,out}-h_{c,in})
\end{equation}
where ( h ) is the specific enthalpy, which accounts for the heat capacities temperature dependence. For constant $C_p$, this simplifies to $m_cC_p\Delta{T}$.
\begin{equation}
h_{c,out}-h_{c,in}\int_{T_{c,out}}^{T_{c,in}}C_p(T)dT
\end{equation}

If the $C_p$ data is discrete data points, one could numerically integrate the data over the interval using any of the numerical integration methods such as Trapezoidal Rule or Simpson's rule. However, in most applications, especially over a narrow temperature range, there simply isn't much variation so this is overkill. Averaging $C_p$ at the inlet and outlet is essentially a shortcut to approximate this integral and is often all that is needed.


There are no strict universal standard for reporting energy balance deviations in heat exchangers, but there are common practices in engineering, especially in testing, research, and industry, that make the results clear and useful. There are four common methods to report energy balance deviation:

\begin{enumerate}
	\item Percentage Difference (relative deviation)
	\item Absolute Difference
	\item Ratio of Heat Transfers
	\item Energy Balance Closure
\end{enumerate}


Here is how it is \textit{usually} approached:

The percent relative deviation for the heat exchanger energy balance is widely used because it's intuitive, accounts for scale and aligns with engineering tolerances. For example, ASME standards for heat exchanger testing (e.g., ASME PTC 12.5 \footnote{American Society of Mechanical Engineers (ASME), "Single Phase Heat Exchangers", ASME PTC 12.5-2000 (R2015)}) often suggest reporting imbalances as a percentage of mean heat transfer.

%This is a statement.\footnote{ASME, "Single Phase Heat Exchangers", asdfasdf}

It is calculated as:

\begin{equation}
	{Deviation (\%)} = \frac{\left| |Q_h| - Q_c \right|}{\frac{|Q_h| + Q_c}{2}} \times 100
\end{equation}

where \( Q_h \) is the heat transfer rate from the hot side (negative, indicating heat loss), \( Q_c \) is the heat transfer rate to the cold side (positive, indicating heat gain), and \( |Q_h| \) is the absolute value of the hot-side heat transfer.
\subsection{Colburn Modulus}
\begin{equation}
	j=St\cdot{Pr^{2/3}}
\end{equation}

\subsection{Friction Factor}

\section{Spreadsheet}

	
\section{Appendix}

\end{document}          
