% CKD in catsasdfadf
\section{Chronic Kidney Disease in Cats}
Chronic kidney disease (CKD) is one of the most common conditions in older cats, affecting up to 30-40\% of cats over 10 years old and even more in those over 15. It occurs when the kidneys gradually lose their ability to filter waste products from the blood, regulate fluids and electrolytes, and perform other vital functions. Unlike acute kidney injury, CKD is progressive and irreversible—once significant damage occurs (often when about two-thirds of kidney function is lost), the kidneys cannot fully recover.

The exact cause is often unknown (idiopathic in many cases), but it can stem from long-term issues like chronic inflammation, infections, toxins, high blood pressure, dental disease, or congenital problems such as polycystic kidney disease in certain breeds. Early stages may show no obvious signs, but as the disease advances, common symptoms include increased thirst and urination, weight loss, reduced appetite, lethargy, vomiting, bad breath, and poor coat condition.

While there is no cure for CKD, early diagnosis through blood tests (checking creatinine, SDMA, and other markers) and urine analysis allows for the best management. The main goals are to slow progression, manage symptoms, and maintain quality of life. Key approaches include feeding a prescription renal diet (low in phosphorus and protein, high in moisture and antioxidants), ensuring excellent hydration (via wet food, water fountains, or subcutaneous fluids), controlling blood pressure and phosphorus levels with medications, treating anemia or nausea when needed, and regular veterinary monitoring.

With proper care, many cats live comfortably for months to years after diagnosis, often enjoying good quality of life well into their senior years. Always consult your veterinarian for tailored advice, as treatment is customized to your cat's stage and needs.

https://cdn.shoplightspeed.com/shops/629248/files/69999934/ref8v19-kidneyhealthcats.pdf



https://web.archive.org/web/20260115053242/https://cdn.shoplightspeed.com/shops/629248/files/69999934/ref8v19-kidneyhealthcats.pdf