\section{How to Make Kidney Yogurt}


The book Super Gut, by reknowned cardiologist Dr. William Davis describes various homemade yogurt concoctions are made by a long fermentation process, usually in a dairy substance such as organic half-and-half. A distinguishing point of this process is the long fermentation time on the order of 36 hours. The fermentation time is designed to produce high colony forming units (CFUs) of whatever probiotic is being fermented. These microbes reproduce asexually so they double according to a time interval, often times as short as 30 minutes but can be 3 or more hours. The double time tends to be a function of temperature and the fermentation environment, including the medium (e.g., half-and-half).

The microbe that has perhaps gotten the most attention is L. Reuteri as it appears to be a keystone microbe that has mostly been lost in modern society due to overuse of antibiotics. L. Reuteri has a double time of three hours which equates to 12 doublings in a 36-hour fermentation cycle.

Subtilis doubles every 20-25 minutes at 37°C. 

\begin{table}[ht]
	\centering
	\begin{tabular}{ll}
		\toprule
		\textbf{Ingredient} & \textbf{Amount} \\
		\midrule
		Organic ultra-pasteurized half-and-half & 1 quart \\
		B. coagulans GBI-30,6086 capsules & 1--2 \\
		Inulin powder (prebiotic) & 2 tbsp \\
		\bottomrule
	\end{tabular}
	\caption{Ingredients for 1 quart batch}
	\label{tab:recipe-ingredients}
\end{table}

Fermentation steps:
\begin{enumerate}[leftmargin=*]
	\item Mix slurry...
	\item Heat and cool...
	\item Ferment at 106°F for 36 hours...
\end{enumerate}